### 2022-05-31 LaTeX/report.tex
Updates

\documentclass[a4 paper, 12pt]{article}
\usepackage{amsmath, amsthm, amsfonts, amssymb, mathrsfs}
\usepackage{tikzit}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}
\usepackage[ruled,vlined, linesnumbered]{algorithm2e}

@@

\subsubsection{\texttt{pre\_dfs} implies \texttt{post\_dfs}}

\subsubsection{Partial correctness}

>>>>

\documentclass[a4 paper, 12pt]{article}
\usepackage{amsmath, amsthm, amsfonts, amssymb, mathrsfs}
\usepackage{tikzit}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{mathtools}
\usepackage[ruled,vlined, linesnumbered]{algorithm2e}

@@

\subsubsection{\texttt{pre\_dfs} implies \texttt{post\_dfs}}\label{lemma:pre_post_dfs}

\subsubsection{Partial correctness}
This lemma shows two things:
\BlankLine
\noindent
\texttt{dfs\_dfss\_dom (Inl(v,e)) $\land$ pre\_dfs v e} $\Longrightarrow$ \texttt{post\_dfs v e (dfs v e)}
\BlankLine
\noindent
\texttt{dfs\_dfss\_dom (Inr(v,e)) $\land$ pre\_dfss v vs e} $\Longrightarrow$ \texttt{post\_dfss v vs e (dfss v vs e)}

\BlankLine
\noindent
where \texttt{dfs\_dfss\_dom (Inl(v,e))} -- respectively \texttt{Inr(v, e)} -- is the assumption that \texttt{v} and \texttt{e} are in the domain of definition of \texttt{dfs} (respectively \texttt{dfss}).
\BlankLine
The first proposition is a consequence of the lemma \nameref{lemma:pre_post_dfs}.
\BlankLine
For the second proposition, we need to write the proof according to the definition of \texttt{dfss}. That is, we need to show the following proposition:

With these assumptions:
\begin{itemize}
    \item $\texttt{dfs\_dfss\_dom} (\texttt{Inr}(v,vs,e))$
    \item $\texttt{pre\_dfss}~v~vs~e$
    \item $vs \neq \varnothing$ and \\$\forall w \in vs,  w \notin \texttt{explored } e~\land~w \notin \texttt{visited } e~\land~\texttt{pre\_dfs}~w~e \Longrightarrow \texttt{post\_dfs}~w~e~(dfs~w~e)$
    \item let $e' =
    \begin{dcases}
		e & w \in \texttt{explored}~e \\
		\texttt{dfs}~v~e & w \in \texttt{visited}~e \\
        \texttt{unite}~v~w~e & \text{otherwise}
	\end{dcases}$\\
    $vs \neq \varnothing$ and \\$\forall w \in vs, \texttt{pre\_dfss}~v~(vs - \{w\})~e' \Longrightarrow \texttt{post\_dfss}~v~(vs - \{w\})~e'~(\texttt{dfss}~v~(vs~-~\{w\})~e')$
\end{itemize}
\noindent
We need to show the post-condition of \texttt{dfss}:
\begin{equation*}
    \texttt{post\_dfss}~v~vs~e~(\texttt{dfss}~v~vs~e)s
\end{equation*}

If the set of successors $vs$ is empty, then the post-condition of \texttt{dfss} is satisfied.
Otherwise, the proof is split according to the cases in the definition of $e'$. In the first case, $w$ is in the set of explored nodes of $e$. Hence, $e' = e$. The proof is rather straightforward thanks to the assumption on \texttt{pre\_dfss}. The following case, \textit{i.e.} $w \in \texttt{visited }e$ is much more complicated. In this case, $e' = \texttt{dfs}~v~e$.
